Workflow for Ecov Recruitment Analysis

### 2024-01-26 Ecov_study/recruitment_functions/Workflow_Ecov_Recruitment_Project.Rmd

7. Cleaning up script **compare_projections.R**
   + evaluates relative error in projections between peel 10 and truth ...
   + Runtime ...
   + **<span style="color: blue;">STATUS: pending... beta unstandardized; </span>**

>>>>

7. Cleaning up script **compare_RE_SD_projections.R**
   + evaluates relative error and log_sd (CV) in projections between peel 10 and truth for recruitment, catch, and ssb
   + summarizes over all 10 years in the projection, and also over just the first 3 years
   + turns out no OM factors made a difference; pretty boring
   + Runtime 1.6 hours
   + **<span style="color: blue;">STATUS: done beta unstandardized; </span>**
